On the probability of finding a nonphysical solution through shadowing

### 2020-10-27 main.tex
Add new figures of pert tent map

Both the nonphysicality of shadowing solutions, and the existence of extremely non-smooth statistical response, undermine the validity of using shadowing for sensitivity analysis of statistics \cite{qiqi-lss}\cite{angxiu-lss}\cite{lasagna}. When the goal is to compute derivatives of ensemble averages, where the ensemble
is distributed according to the physical measure, i.e., the SRB measure, shadowing-based methods can give wrong results. This is because shadowing-based methods compute the sensitivities of ensemble statistics along shadowing solutions, but these may not be physical solutions that reproduce ensemble statistics. The error in shadowing sensitivities has been observed
before and appropriately attributed as ``ergodicity breaking error'' \cite{patrick} \cite{angxiu-error}. 
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{osc_tent_n.png}
    \includegraphics[width=0.45\textwidth]{osc_tent_s.png}
    \caption{The plucked tent map shown at different values of $s$ and $n$, that represent the magnitude and frequency of the applied oscillation to the original tent map ($n=0,s=0$). On the left, $s$ is held constant at 0.5. On the right, $n$ is held constant at 0.}
    \label{fig:pluckedTentMap}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{osc_tent_dens_0.1_0.png}
    \includegraphics[width=0.45\textwidth]{osc_tent_dens_0.1_6.png}
    \caption{The effect of increasing $n$ on the probability distribution associated to the plucked tent map. L: The stationary probability distribution of the plucked tent map at $s=0.1, n = 0$. R: The stationary probability distribution of the plucked tent map at $s=0.1, n = 6$.}
    \label{fig:pluckedTentMapDistribution}
\end{figure}
Violations of smooth response, like in the plucked tent map, have an immediate implication for shadowing sensitivities as well. In particular, if perturbed solutions are shadowed by physical solutions for all time, the change in the statistics of the perturbed solutions must be small. In other words, the physicality of shadowing predicts that there cannot be a large change in statistics due to small parameter perturbations; the reality is that, as illustrated by the plucked tent map, the effect of small parameter changes on the statistics can be drastic.

>>>>

Both the nonphysicality of shadowing solutions, and the existence of extremely non-smooth statistical response, undermine the validity of using shadowing for sensitivity analysis of statistics \cite{qiqi-lss}\cite{angxiu-lss}\cite{lasagna}. When the goal is to compute derivatives of ensemble averages, where the ensemble
is distributed according to the physical measure, i.e., the SRB measure, shadowing-based methods can give wrong results. This is because shadowing-based methods compute the sensitivities of ensemble statistics along shadowing solutions, but these may not be physical solutions that reproduce ensemble statistics. The error in shadowing sensitivities has been observed
before and appropriately attributed as ``ergodicity breaking error'' \cite{patrick} \cite{angxiu-error}. 
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{osc_tent_0.png}
    \includegraphics[width=0.45\textwidth]{osc_tent_3.png}
    \includegraphics[width=0.45\textwidth]{osc_tent_6.png}
     \includegraphics[width=0.45\textwidth]{osc_tent_10.png}
    \caption{The plucked tent map shown at different values of $s$ and $n = 0$ (top-left), $n=3$ (top-right), $n=6$ (bottom-left), and $n=10$ (bottom-right). The original tent map is at $s=0$ on each plot.}
    \label{fig:pluckedTentMap}
\end{figure}
\begin{figure}
    \centering
%    \includegraphics[width=0.45\textwidth]{osc_tent_dens_0.png}
 %   \includegraphics[width=0.45\textwidth]{osc_tent_dens_3.png}
  %  \includegraphics[width=0.45\textwidth]{osc_tent_dens_6.png}
   % \includegraphics[width=0.45\textwidth]{osc_tent_dens_10.png}
    \caption{The effect of increasing $n$ on the probability distribution associated to the plucked tent map. L: The stationary probability distribution of the plucked tent map at $s=0.1, n = 0$. R: The stationary probability distribution of the plucked tent map at $s=0.1, n = 6$.}
    \label{fig:pluckedTentMapDistribution}
\end{figure}
Violations of smooth response, like in the plucked tent map, have an immediate implication for shadowing sensitivities as well. In particular, if perturbed solutions are shadowed by physical solutions for all time, the change in the statistics of the perturbed solutions must be small. In other words, the physicality of shadowing predicts that there cannot be a large change in statistics due to small parameter perturbations; the reality is that, as illustrated by the plucked tent map, the effect of small parameter changes on the statistics can be drastic.
